### 2019-06-05 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Proofreading of all Ch2 and Ch3

% ----------------------------------------------------------------------
% \subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
\paragraph{Notations.}\label{sub:25:aggregation}

@@

% ----------------------------------------------------------------------
\paragraph{Explanations of \Aggr{} versus \ExpQ{} .}\label{sub:25:Exp4}

@@

\paragraph{How to choose the learning rates $(\eta_t)$?}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), the best choice is given by $\eta_t = \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic\footnote{~For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}.} to assume a fixed and known time horizon, so we prefer the alternative horizon-free choice%
\footnote{~It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.}
of learning rates,
$\eta_t = \log(N) / (t K)$ suggested by \cite{Bubeck12}.
We compare both approaches empirically, and the second one usually performs better.
We also stick to this choice of $(\eta_t)_{t \geq 1}$ for \Aggr.

@@

% - explain the problem studied in the simulation
We focus on \emph{i.i.d.} MAB problems, with $K = 9$ channels\footnote{~Similar behaviors are observed for other values, \eg, trying up-to $K = 100$ gave the same results.}.
For Bernoulli problem, the first one uses $\boldsymbol{\mu}=[0.1,\dots,0.9]$, and is considered as a ``simple'' problem.
The second one is divided in three groups:
2 very bad arms ($\mu = 0.01, 0.02$), 5 average arms ($\mu = 0.3$ to $0.6$) and 3 very good arms ($\mu = 0.78, 0.8, 0.82$), and it is considered as a ``harder'' problem.
The horizon is set to $T = 20000$ (but its value is unknown to all algorithms), and simulations are repeated $1000$ times, to estimate the expected regret.
%
This empirical estimation of the expected regret $R_T$ is plotted below, as a function of $T$, comparing some algorithms $\Alg_1,\dots,\Alg_N$ (for $N=6$), and their aggregation with \Aggr{} (displayed in orange bold),
using the parameter-free learning rate sequence, $\eta_t = \log{N} / (t K)$.

The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted.
It corresponds to the second case in Theorem~\ref{thm:2:secondLogTLowerBound}.
It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli}).

@@

This would be a first theoretical guarantee, but not satisfactory as we saw above that simple algorithms (like \UCB) have regrets scaling as $\log(T)$ \cite{Auer02,Bubeck12}, not $\sqrt{T}$.
%
Regret bounds in several different settings are proved for the \CORRAL{} algorithm \cite{Agarwal16}, but no logarithmic upper-bound can be obtained from their technique, even in the simplest setting of stochastic bandits.
%
However, \Aggr{} always seems to have a (finite-horizon) logarithmic regret in all the experiments we performed,
for both Bernoulli and non-Bernoulli problems (\eg, Gaussian, exponential and Poisson distributions).
Further theoretical developments were left as future work.

>>>>

% ----------------------------------------------------------------------
% \subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
\textbf{Notations:}\label{sub:25:aggregation}

@@

% ----------------------------------------------------------------------
\textbf{Comparison with \ExpQ{}:}\label{sub:25:Exp4}

@@

\textbf{How to choose the learning rates $(\eta_t)$:}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), the best choice is given by $\eta_t = \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic\footnote{~For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}.} to assume a fixed and known time horizon, so we prefer the alternative horizon-free choice%
\footnote{~It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.}
of learning rates,
$\eta_t = \log(N) / (t K)$ suggested by \cite{Bubeck12}.
We compare both approaches empirically, and the second one usually performs better.
We also stick to this choice of $(\eta_t)_{t \geq 1}$ for \Aggr.

@@

% - explain the problem studied in the simulation
We focus on \emph{i.i.d.} MAB problems, with $K = 9$ channels\footnote{~Similar behaviors are observed for other values, \eg, trying up-to $K = 100$ gave the same results.}.
For Bernoulli problem, the first one uses $\boldsymbol{\mu}=[0.1,\dots,0.9]$, and is considered as a ``simple'' problem.
The second one is divided in three groups:
2 very bad arms ($\mu = 0.01, 0.02$), 5 average arms ($\mu = 0.3$ to $0.6$) and 3 very good arms ($\mu = 0.78, 0.8, 0.82$), and it is considered as a ``harder'' problem.
The horizon is set to $T = 20000$ (but its value is unknown to all algorithms), and simulations are repeated $1000$ times, to estimate the expected regret.
%
This empirical estimation of the expected regret $R_T$ is plotted below\footnote{~The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted. It corresponds to the second case in Theorem~\ref{thm:2:secondLogTLowerBound}. It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli}).},
as a function of $T$, comparing some algorithms $\Alg_1,\dots,\Alg_N$ (for $N=6$), and their aggregation with \Aggr{} (displayed in orange bold),
using the parameter-free learning rate sequence, $\eta_t = \log{N} / (t K)$.

@@

This would be a first theoretical guarantee, but not satisfactory as we saw above that simple algorithms (like \UCB) have regrets scaling as $\log(T)$ \cite{Auer02,Bubeck12}, not $\sqrt{T}$.
%
Regret bounds in several different settings are proved for the \CORRAL{} algorithm \cite{Agarwal16}, but no logarithmic upper-bound can be obtained from their technique, even in the simplest setting of stochastic bandits.
%
However, \Aggr{} always seems to have a (finite-horizon) logarithmic regret in all the experiments we performed,
for both Bernoulli and non-Bernoulli problems (\eg, Gaussian, exponential and Poisson distributions).
% Further theoretical developments were left as future work.
